---
title: "Week 1 Exercises"
author: "Nicholas Scrofano"
date: "March 19, 2023"
output:
  word_document: default
  pdf_document: default
---

Please complete all exercises below WITHOUT using any libraries/packages.

# Exercise 1
Assign 10 to the variable x. Assign 5 to the variable y. Assign 20 to the variable z.

```{r ex1}
x <- 10

y <- 5

z <- 20


```


# Exercise 2
Show that x is less than z but greater than y.

**Note: your output must be a SINGLE boolean, do not output a boolean for each expression.**

```{r ex2}
# x is greater than y and x is less than z
y < x & x < z

```

# Exercise 3
Show that x and y do not equal z. 

**Note: your output must be a SINGLE boolean, do not output a boolean for each expression.**

```{r ex3}
# x and y do not equal z
x & y != z

```


# Exercise 4
Show that the formula `x + 2y = z`. 

**Note: your output must be a SINGLE boolean**

```{r ex4}
# z is equal to x plus 2 times y

z == x + 2*y

```

# Exercise 5
I have created a vector (test_vector) of integers for you. Determine if any of x, y, or z are in the vector. 

**Note: your output must be a SINGLE boolean, do not output a boolean for each expression.**


```{r ex5}
test_vector <- c(1,5,11:22)

# is the value x or y or z contained in test_vector

x | y | z %in% test_vector

```

# Exercise 6
Show which value is contained in the test vector. To do this you will need to create an element-wise logical vector using operators. `x == vector`. Once you have done that you will need to use slicing to return all indices that have matches.
**Note: your output should be two integers**

```{r ex6}

# Determine which of x y and z are in the test vector

test_vector <- c(1,5,11:22)

x %in% test_vector
y %in% test_vector
z %in% test_vector

# Returning indices that have matches

test_vector[test_vector == y]
test_vector[test_vector == z] 


```

